FOOBAR: Web-based Data Analytics in Haskell

### 2011-12-16 paper/paper.tex
Two things missing from the last commit.

@@

Persistent deals with types by having a restricted set of types that it uses to interface with the database, the \code{PersistValue} type.  These types closely resemble JSON or BSON types, as it includes a few primatives, null, and the two collection types \code{PersistList [PersistValue]} and \code{PersistMap [(Text, PersistValue)].  The library ensures that the backend can store values of these types to limit dependencies and coupling between the application data types and the database's internal representation.

>>>>

% For representing code in paragraphs.
\newcommand{\code}[1]{\texttt{#1}}

@@

Persistent deals with types by having a restricted set of types that it uses to interface with the database, the \code{PersistValue} type.  These types closely resemble JSON or BSON types, as it includes a few primatives, null, and the two collection types \code{PersistList [PersistValue]} and \code{PersistMap [(Text, PersistValue)]}.  The library ensures that the backend can store values of these types to limit dependencies and coupling between the application data types and the database's internal representation.
